Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-17 papers/EMNLP2019/modeling.tex
Figures->figures; results in modeling

\paragraph{Measures}
top: the model's top prediction
\begin{itemize}
	\item \textbf{top=VG} The average model accuracy on the VG names
	\item \textbf{top=MN-1} The average model accuracy on the top response in ManyNames
	\item \textbf{top$\in$MN} The average model accuracy to predict any name of the responses in ManyNames
	\item \textbf{KL} The average Kullback-Leibler divergence of the model's softmax output and the  distribution over ManyNames, estimated by normalizing the name counts per instance
\end{itemize}

We further compare the model on the set of instances where the VG names does not match the top response in MN.

Sets of instances: all images, not training, only those with VG != MN-1.

\paragraph{Results} 
\begin{table*}
	\small
	\begin{tabular}{l@{~}|rrrr|rrrr|rrrr}
				 &	\multicolumn{4}{c|}{All images ($24,585$)} 
				 & \multicolumn{4}{c|}{Images w/ VG != MN-1 ($6,280$)}
				 & \multicolumn{4}{c}{$\neg$Train images ($2,281$)} \\
		domain	 &  top=VG & top=MN-1 & top$\in$MN  &  KL
					&  top=VG & top=MN-1 & top$\in$MN  & KL
					&  top=VG & top=MN-1 & top$\in$MN  & KL\\
		\toprule
		all 	& 68.7 & 76.8 & 94.8 & 
				& 20.7 & 52.5 & 92.3 & 
				& 63.5	& 73.1	& 92.5 &\\
		\midrule
		... \\
		\bottomrule
	\end{tabular}
	\caption{Blabla	\label{tab:model}}
\end{table*}
\iffalse
Total sum of differences after score conversion to relevant classes: 156.810 (avg=0.006378)
Evaluation on VG (24585 instances):
Accuracy (top VG): 0.686678869229 (t: 16882, f: 7703, not found: 0)
Evaluation on YNI-1 (24585 instances):
Accuracy (top1 YNI): 0.768069961359 (t: 18883, f: 5702, not found: nan)
Evaluation on YNI-10 (24585 instances):
Accuracy (top10 YNI): 0.947813707545 (t: 23302, f: 1283, not found: nan)

Evaluation on VG -- only instances where topYNI != VG (6280):
Accuracy (top VG): 0.207006369427 (t: 1300, f: 4980, not found: 0)
Evaluation on YNI-1 -- only instances where topYNI != VG (6280):
Accuracy (top1 YNI): 0.525636942675 (t: 3301, f: 2979, not found: nan)
Evaluation on YNI-10 -- only instances where topYNI != VG (6280):
Accuracy (top10 YNI): 0.922929936306 (t: 5796, f: 484, not found: nan)

Evaluation VG on training images (22304)
Accuracy (top VG): 0.691983500717 (t: 15434, f: 6870, not found: 0)
Evaluation YNI-1 on training images (22304)
Accuracy (top1 YNI): 0.771879483501 (t: 17216, f: 5088, not found: nan)
Evaluation YNI-10 on training images (22304)
Accuracy (top10 YNI): 0.950098637016 (t: 21191, f: 1113, not found: nan)

Evaluation VG on NOT training images (2281)
Accuracy (top VG): 0.634809294169 (t: 1448, f: 833, not found: 0)
Evaluation YNI-1 on NOT training images (2281)
Accuracy (top1 YNI): 0.73081981587 (t: 1667, f: 614, not found: nan)
Evaluation YNI-10 on NOT training images (2281)
Accuracy (top10 YNI): 0.925471284524 (t: 2111, f: 170, not found: nan)

\fi

>>>>

\paragraph{Measures}
\textsl{top}: the model's top prediction
\begin{itemize}
	\item \textbf{=VG} The average model accuracy of \textsl{top} on the VG names
	\item \textbf{=MN-1} The average model accuracy of \textsl{top} on the top response in ManyNames
	\item \textbf{$\in$MN} The average model accuracy of \textsl{top} to match any name of the responses in ManyNames
	\item \textbf{KL} The average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ of the model's softmax output~$S$ and the  probability distribution~$M$ over ManyNames, estimated by normalizing the name counts per instance
\end{itemize}

\paragraph{Results} 
We compare the model against a random baseline for the KL divergence, and against a most-frequent name baseline. 
We further compare the model on the set of instances where the VG names does not match the top response in MN (block \mbox{VG$\neq$MN-1} in Table~\ref{tab:model}), and to those which were not part of the set of images used for training bottom-up ($\neg$Training).
%
\begin{table*}
	\centering
	\small
\begin{tabular}{l@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr}
	\toprule
	%{} &  All images-top=VG &  All images-top=MN-1 &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN-1 &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN-1 &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
		& \multicolumn{12}{c}{Image subset} \\
		&	\multicolumn{4}{c}{All ($24,585$)} 
		& \multicolumn{4}{c}{VG$\neq$MN-1 ($6,280$)}
		& \multicolumn{4}{c}{$\neg$Training ($2,281$)} \\
	\midrule
		Domain	 &  =VG & =MN-1 & $\in$MN  &  KL
		&  =VG & =MN-1 & $\in$MN  & KL
		&  =VG & =MN-1 & $\in$MN  & KL\\
\midrule
all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\ \\
home           &               70.0 &                 74.7 &                   93.4 &            1.1 &            24.3 &              47.5 &                91.4 &         1.4 &             67.2 &               70.5 &                 92.5 &          1.2 \\
food           &               60.0 &                 71.9 &                   87.7 &            1.0 &            14.2 &              48.9 &                76.6 &         1.5 &             46.6 &               62.1 &                 80.1 &          1.3 \\
buildings      &               57.5 &                 70.7 &                   92.1 &            1.3 &             7.9 &              63.4 &                89.8 &         1.5 &             44.3 &               60.2 &                 88.6 &          1.4 \\
vehicles       &               69.8 &                 72.8 &                   97.6 &            0.6 &            35.3 &              46.1 &                97.4 &         0.7 &             67.2 &               73.5 &                 96.4 &          0.7 \\
animals/plants &               92.7 &                 94.8 &                   97.7 &            0.4 &            20.3 &              65.0 &                94.0 &         0.9 &             91.3 &               92.6 &                 96.2 &          0.5 \\
clothing       &               63.3 &                 70.9 &                   92.6 &            1.0 &            19.9 &              48.5 &                90.3 &         1.2 &             50.8 &               60.2 &                 87.4 &          1.3 \\
people         &               48.5 &                 70.7 &                   95.5 &            1.2 &            13.8 &              58.9 &                95.3 &         1.3 &             42.2 &               68.2 &                 92.8 &          1.2 \\
\bottomrule
%Baseline      &                3.3 &                  5.2 &                   12.0 &            -- &             1.7 &               9.3 &                21.8 &         -- &              3.0 &                5.0 &                 11.9 &          -- \\
Baseline       &                3.9 &                  4.6 &                    5.6 &            -- &             0.1 &               3.0 &                 3.8 &         -- &              3.8 &                4.6 &                  5.8 &          -- \\
\end{tabular}
\caption{Baseline: The most frequent name. Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN-1) and 6.9 ($\neg$Training)	\label{tab:model}}
\end{table*}
